\article{Management Committee}

\section{Purpose of the Management Committee}
The administration of the Club shall be vested in the Management Committee, which shall be elected in accordance with the provisions of the NUSSU Constitution, NUSSU Regulations, this Constitution and the Club's Election Standing Order (ESO).

\section{Composition of the Management Committee}
The Management Committee is made up of the:
	\begin{itemize}
	\item Presidential Cell (PCell) which consists of the:
		\begin{itemize}
		\item President
		\item Vice-President (External Relations)
		\item Vice-President (Operations \& Projects)
		\item Vice-President (Human Resource \& Development)
		\end{itemize}
		
	\item Secretariat which consists of the:
		\begin{itemize}
		\item General Secretary and Assistant General Secretary
		\item Two Financial Secretaries
		\item Student Relations Secretary and Assistant Student Relations Secretary
		\end{itemize}
		
	\item External Relations Wing shall be led by the Vice-President (External Relations) and consists of the following members:
		\begin{itemize}
		\item Director and Deputy Director of Marketing
		\item Director and Deputy Director of Publicity
		\item Director and Deputy Director of Alumni Relations
		\end{itemize}
		
	\item Operations and Projects Wing shall be let by Vice-President (Operations and Projects) and consists of the following members:
		\begin{itemize}
		\item Director and Deputy Director of Logistics
		\item Director and Deputy Director of Information Technology
		\item Director and Deputy Director of Freshmen Orientation Projects
		\end{itemize}
		
	\item Human Resource and Development Wing shall be led by the Vice-President (Human Resource and Development) and consists of the following members:
		\begin{itemize}
		\item Director and Deputy Director of Welfare
		\item Director and Deputy Director of Sports
		\item Director and Deputy Director of Academic Liaison
		\end{itemize}
	\end{itemize}

\section{Term of Office}
Members of the Management Committee shall hold office from the day they are elected or co-opted to thirty (30) calendar days after the election of the next Management Committee.
	\begin{legal}
	\item The Management Committee members shall not leave Singapore for
		\begin{legal}
		\item More than two (2) weeks during the December School Vacation Period, and
		\item More than one (1) month during the June School Vacation Period.
		\end{legal}
	
	\item The Management Committee members shall not go on
		\begin{legal}
		\item Student Exchange Programme (SEP),
		\item NUS Overseas College (NOC or ATAP), during their Term of Office, or
		\item Any other programme which requires participation away from office for a period of more than 2 months or impeding their duties as a Management Committee.
		\end{legal}
	
	\item However, the Management Committee members may be exempted from Clause IV.3.1 and Clause IV.3.2 above if given the majority approval of the Presidential Cell of the Management Committee and endorsement of the Club Advisors.
		\begin{legal}
		\item Should the Management Committee member be from the Presidential Cell, approval should be sought from the School of Computing Dean.
		\item Any Management Committee member who fails to follow Clause IV.3.1 and Clause IV.3.2 will automatically be relieved from his/her appointment.
		\end{legal}
	\end{legal}

\section{Functions of the Management Committee}
The Management Committee shall
	\begin{legal}
	\item be responsible for the formulation of policies and organization of activities which are consistent with the objectives of the Club;
	\item have charge of the properties of the Club;
	\item be responsible for the proper expenditure of the Club's finances in accordance with an approved budget;
	\item publish an annual report on the Club's activities, which shall also include the annual accounts for the Club; and
	\item facilitate the handover of duties to the next Management Committee.
	\end{legal}

\section{Powers of the Management Committee}
The Management Committee shall have the following powers:
	\begin{legal}
	\item to elect Council Representatives from among its members to the Union Council in accordance with the provisions of the NUSSU Constitution and NUSSU Regulations;
	\item to consider the provisional annual budget prepared by the Financial Secretary for the period 1 October to 30 September prior to its submission to the Office of Financial Services;
	\item to appoint standing or special committees for the proper administration of the Club and to exercise control over such committees;
		\begin{legal}
		\item to delegate to such committees such powers as it consider necessary;
		\end{legal}
	\item to accept the resignation of any Member of the Management Committee;
		\begin{legal}
		\item to accept the resignation of any Council Representative or member of the Management Committee and to fill, in accordance with the NUSSU Constitution, NUSSU Regulations, this Constitution and the Club's ESO, the vacancy thus arising;
		\end{legal}
	\item to take disciplinary action against Members who violate the Constitution of the Club;
	\item to release publications and official statements on behalf of the Club, such publications and statements to be consistent with the objectives of the Club.
		\begin{legal}
		\item Any official statement shall only be made by the President or the General Secretary, and only with the approval of the Management Committee.
		\item No publication may be released without the approval of Vice-President (External Relations).
		\item All publications and official statements shall be in the name of the Club and not the National University of Singapore Students' Union, notwithstanding the fact that the Club is a Constituent Body of the Union.
		\end{legal}
	\item to give a decision upon any matter consistent with the objectives of the Club but not provided for in this Constitution;
	\item to request for Extraordinary Management Committee Meeting in accordance to Article IV.8;
	\item to co-opt members for the proper administration of the Club, subject to the following:
		\begin{legal}
		\item Such co-opted members shall sit on the Management Committee and hold office until one month after the election of the next Management Committee.
		\item The total number of elected members of the Management Committee, shall not exceed twenty (20), in accordance to NUS Regulation 9.
		\item Co-opted members shall be deemed to be members of the Management Committee and be accorded the same rights and duties as elected members, with the exception of the right to vote.
		\item However, subject to IX.5.2, any co-opted member may only be given the right to vote at Management Committee Meetings if a motion is passed during the General Meeting to give him/her voting rights.
		\item Co-option of members shall be passed with majority vote by the Management Committee Members with voting rights during a Management Committee Meeting.
		\end{legal}
	\end{legal}

\section{Types of Meetings of the Management Committee}
A meeting of the Management Committee shall be either an Ordinary Management Committee Meeting or an Extraordinary Management Committee Meeting.

\section{Frequency of Meetings of the Management Committee}
Ordinary Management Committee Meetings shall be held at least three (3) times in a term.
	\begin{legal}
	\item The General Secretary shall give at least seven (7) days' notice of such meetings
	\item Members of the Management Committee shall give at least three (3) days' notice to the General Secretary of amendments to the agenda.
	\item The date and time of such meetings shall be determined by the President but the first of such meetings shall be held no later than two (2) weeks of the Management Committee being elected into office.
	\end{legal}

\section{Extraordinary Meetings of the Management Committee}
Extraordinary Management Committee Meetings shall be held whenever matters requiring urgent attention arise or when a written request signed by at least three (3) members of the Management Committee is received by the General Secretary.
	\begin{legal}
	\item Only the matter for which the Extraordinary Management Committee Meeting is called shall be on the agenda.
	\item An Extraordinary Management Committee Meeting shall be convened by the General Secretary within seven (7) days of the receipt of the written request for the meeting.
	\end{legal}

\section{Quorum for Meetings of the Management Committee}
At least half (1/2) the existing members of the Management Committee who have voting rights shall constitute a quorum.
	\begin{legal}
	\item Quorum must be met before a motion can be raised, and the quorum must be maintained before any motion is voted on.
	\item Only the voting members present for the entirety of said motion being addressed shall constitute the quorum, in accordance to IV.9 herein.
	\end{legal}

\section{Chairman of Meetings of the Management Committee}
The President shall be the Chairman at every Management Committee Meeting.
	\begin{legal}
	\item In the absence of the President, the General Secretary shall appoint a Chairman (who shall not be the General Secretary) from among the members of the Management Committee.
	\end{legal}

\section{Replacement of President}
In the event the position of President becomes vacant:
	\begin{legal}
	\item Either a Vice-President shall be internally elected by the Management Committee to succeed the President for the remainder of the President's term of office
		\begin{legal}
		\item The newly elected President shall resign from his original position in the Management Committee before taking up the position of the President.
		\end{legal}
	\item Or the position may be filled in a General Meeting.
	\end{legal}

\section{Replacement of Vice-President}
In the event that the position of a Vice-President is vacant:
	\begin{legal}
	\item Either a member of the Management Committee shall be internally elected by the Management Committee to succeed the Vice-President for the remainder of the Vice-President's term of office.
	\begin{legal}
		\item The newly elected Vice-President shall resign from his original position in the Management Committee before taking up the position of the Vice-President.
	\end{legal}
	\item Or the position may be filled in a General Meeting.
	\end{legal}

\section{Replacement of Director}
In the event that the position of a Director becomes vacant:
	\begin{legal}
	\item The Deputy Director will be promoted to Director.
	\item In the event that there is no Deputy Director, a new Director shall be co-opted in.
	\item In the event that no replacement can be found, the Vice-President in charge of the cell shall serve as the acting Director.
	\end{legal}

\section{Replacement of General Secretary or Student Relations Secretary}
In the event that the position of General Secretary and/or Student Relations Secretary becomes vacant:
	\begin{legal}
	\item The Assistant Secretary will be promoted to Secretary.
	\item In the event that there is no Assistant Secretary, a new Secretary shall be co-opted in.
	\end{legal}

\section{Replacement of Financial Secretary}
In the event that the position of Finance Secretary becomes vacant:
	\begin{legal}
	\item A new Finance Secretary shall be co-opted in.
	\end{legal}