\article{General Meetings of the Club}

\section{}
General Meetings shall be convened by the General Secretary.

\section{}
General Meetings may be either the Annual General Meeting or Extraordinary General Meetings.

\section{}
The Annual General Meeting shall be held no later than the last week of September.
	\begin{legal}
	\item Notice of the Annual General Meeting shall be given to Members no less than ten (10) days before the date of the Meeting.
	\item Any business for discussion on at the Annual General Meeting shall be handed in, in writing, by any five (5) Members, to the General Secretary not less than one (1) week before the time of the Meeting.
		\begin{legal}
		\item The General Secretary may, in his absolute discretion, decline to add in any of such business for discussion at the Annual General Meeting.
		\item However, the Members attending the Annual General Meeting may opt to include such business for discussion at the Annual General Meeting provided such business is ratified by the votes of no less than half (1/2) of the total number of Members present and voting.
		\end{legal}
	\end{legal}

\section{}
An Extraordinary General Meeting is a General Meeting that is not the Annual General Meeting.
	\begin{legal}
	\item An Extraordinary General Meeting shall be convened by the General Secretary either –
		\begin{legal}
		\item on the instruction of the President; or
		\item on the instruction of the Management Committee; or
		\item at the written request of no less than twenty (20) Members of the Club together with a written statement of the object(s) for which the General Meeting is called.
		\end{legal}
	\item An Extraordinary General Meeting shall be held within seven (7) working days of the receipt of the request for the Meeting by the General Secretary.
	\item Notice of an Extraordinary General Meeting shall be posted up no less than three (3) days before the date of the meeting.
	\item Extraordinary General Meeting may be convened during any time of the calendar year.
	\item Only the matter(s) for which the Extraordinary General Meeting is called shall be on the agenda.
	\end{legal}

\section{}
The General Meeting shall have the power to:
	\begin{legal}
	\item fill Management Committee positions that are unfilled; and
		\begin{legal}
		\item The elected member will receive the rights and powers of a co-opted member in accordance to clause IV.5.9 herein.
		\end{legal}
	\item give or remove voting rights during Management Committee Meetings to co-opted Management Committee Members.
		\begin{legal}
		\item Such motions shall be on an individual basis and not give two (2) or more co-opted members voting rights in a single motion.
		\item Such voting rights shall last until the end of his term of office unless subsequently revoked by the Club in a General Meeting.
		\end{legal}
	\item remove Management Committee members from their position through a vote of no confidence.
	\item vote for amendments to the Constitution in accordance with Article XI.
	\end{legal}

\section{}
A vote for censure or of no confidence on the Management Committee or on any Management Committee member may be taken at any General Meeting, provided it is on agenda for that Meeting.
\begin{legal}
	\item Consultation with the Club Advisors must be made before such a request could be handed in to the General Secretary, to be placed on the agenda of the General Meeting.
	\item Such a request shall be handed in, in writing by not less than fifty voting members or five percent of the voting members, whichever is less, of the Club, to the General Secretary not less than seven days before the date of the Meeting.
	\item In such an event and at the same General Meeting, the Club shall hold an election for a new Management Committee or another Management Committee member for the remainder of the term of office of the Management Committee or of the member, as the case may be.
	\end{legal}

\section{}
In the event of the Management Committee intending to resign en bloc, it shall do so only to the Club at an Extraordinary General Meeting to be convened for this purpose. The Club shall then elect a new Management Committee at the same Extraordinary General Meeting to hold office for the remainder of the term of office of the Management Committee.

\section{}
General Meeting Quorum
	\begin{legal}
	\item At least fifty members or five percent of the members, whichever is less, present at the commencement of a Meeting, shall constitute a quorum.
	\item In the event of the required number not being present, the Meeting may proceed with its agenda except for motions stated in X.5, X.6 and X.7 herein.
	\item Quorum must be met before a motion can be raised, and the quorum must be maintained before being voted on.
		\begin{legal}
		\item Only the voting members present for the entirety of said motion being addressed shall constitute the quorum, in accordance to X.8.1 herein.
		\end{legal}
	\end{legal}

\section{}
Motions in a General Meeting shall be carried by the votes of not less than half of the total number of Members present and voting.

\section{}
No Member shall vote by proxy at a General Meeting.

\section{}
All decisions made at General Meetings shall be binding on the Management Committee and Members of the Club.