\article{Committees}

\section{}
There shall be an Election Committee constituted in accordance to the relevant NUSSU Regulations and the Club's ESO.

\section{}
The members of the Election Committee shall be approved by a motion raised in a Management Committee meeting.

\section{}
The Finance Committee shall consist of the following:
	\begin{legal}
	\item the Chairperson of the Committee;
	\item finance Committees of projects under the Club.
	\end{legal}

\section{}
The duties of the Finance Committee shall be to –
	\begin{legal}
	\item maintain the financial records of the relevant committees;
	\item ensure financial accountability;
	\item ensure the Club follows financial regulations as stipulated by the Office of Financial Services.
	\end{legal}

\section{}
The Finance Committee shall have the power to –
	\begin{legal}
	\item approve or reject purchase requests by their relevant committees.
	\end{legal}

\section{}
The Marketing Committee shall consist of the following:
	\begin{legal}
	\item the Chairpersons of the Committee;
	\item recruited members from the Club;
	\item marketing committees of projects under the Club.
	\end{legal}

\section{}
The duties of the Marketing Committee shall be to –
	\begin{legal}
	\item support the branding efforts of the Club;
	\item support marketing efforts for any project under the Club;
	\item generate income for the Club.
	\end{legal}

\section{}
The Marketing Committee shall have the power to –
	\begin{legal}
	\item request, accept or reject sponsorships on behalf of the Club.
	\end{legal}

\section{}
The Publicity Committee shall consist of the following:
	\begin{legal}
	\item the Chairpersons of the Committee;
	\item recruited members from the Club;
	\item publicity committees of projects under the Club.
	\end{legal}

\section{}
The duties of the Publicity Committee shall be to –
\begin{legal}
	\item be responsible for the production of any publication which the Management Committee may direct;
		\begin{legal}
		\item all such publications are to be in accordance with the provisions of Article IV.5 (6) herein;
		\end{legal}
	\item support publicity efforts for any project under the Club.
	\end{legal}

\section{}
The Publicity Committee shall have the power to –
	\begin{legal}
	\item release publications on behalf of the Club in accordance with the provisions of Article IV.5 (6) herein.
	\end{legal}

\section{}
The Alumni Relations Committee shall consist of the following:
	\begin{legal}
	\item the Chairpersons of the Committee;
	\item recruited members from the Club.
	\end{legal}

\section{}
The duties of the Alumni Relations Committee shall be to –
	\begin{legal}
	\item cultivate and promote alumni culture amongst members of the club;
	\item smoothen club members' transition to alumni, with possible collaboration with SoC Student Life, CAA, and Office of Alumni Relations (OAR);
	\item manage relations between members of the Club and SoC alumni.
	\end{legal}

\section{}
The Alumni Relations Committee shall have the power to –
	\begin{legal}
	\item represent the Club at CAA meetings.
	\end{legal}

\section{}
The Logistics Committee shall consist of the following:
	\begin{legal}
	\item the Chairpersons of the Committee;
	\item recruited members from the Club;
	\item logistics committees of projects under the Club.
	\end{legal}

\section{}
The duties of the Logistics Committee shall be to –
	\begin{legal}
	\item book facilities on behalf of the Club;
	\item support logistics efforts for any project under the Club;
	\item be responsible for proper administration of facilities as may be assigned to the Club by the University;
	\item manage the physical assets of the Club.
	\end{legal}

\section{}
The Logistics Committee shall have the power to –
	\begin{legal}
	\item purchase logistical items;
		\begin{legal}
		\item Approval shall be sought in accordance to Article VII.3.1 before making purchases.
		\end{legal}
	\item book facilities on behalf of the Club.
	\end{legal}

\section{}
The IT Committee shall consist of the following:
	\begin{legal}
	\item the Chairpersons of the Committee;
	\item recruited members from the Club.
	\end{legal}

\section{}
The duties of the IT Committee shall be to –
	\begin{legal}
	\item manage IT infrastructure for the Club
	\item assist any project under the Club in terms of IT support
	\end{legal}

\section{}
The Welfare Committee shall consist of the following:
	\begin{legal}
	\item the Chairpersons of the Committee;
	\item recruited members from the Club.
	\end{legal}

\section{}
The duties of the Welfare Committee shall be to –
	\begin{legal}
	\item improve the welfare of members of the Club
	\item inform the Club of any problem within the University that is affecting the welfare of the Club's members.
	\end{legal}

\section{}
The Sports Committee shall consist of the following:
	\begin{legal}
	\item the Chairpersons of the Committee;
	\item recruited members from the Club.
	\end{legal}

\section{}
The duties of the Sports Committee shall be to –
	\begin{legal}
	\item promote health and fitness to the members of the Club, with possible collaboration with Sports Club;
	\item facilitate the participation of the Club in IFG.
	\end{legal}

\section{}
The Academic Liaison Committee shall consist of the following:
	\begin{legal}
	\item the Chairpersons of the Committee;
	\item recruited members from the Club.
	\end{legal}

\section{}
The duties of the Academic Liaison Committee shall be to –
	\begin{legal}
	\item promote the academic interests and facilitate the academic pursuits of members of the Club;
	\item inform the Club of any problem within the University that is affecting the academics of the Club's members.
	\end{legal}
